---
title: "Bot Sleuth_Qualtrics Data Test_6.05.2026"
author: "Abbie Clapp and Michelle Marji"
date: "2026-03-11"
output: html_document
editor_options: 
  chunk_output_type: inline
---

**This version tests the code, including portions that use Qualtrics data, with AC's previous dataset**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Packages
library(httr)
library(jsonlite)
library(purrr)
library(maps)
library(scales)
library(tidyverse)
library(tibble)
library(tidyr)
```

# Data

```{r}
ip_locations_raw <- read_csv("~/Documents/R Files/POP2/Raw Data/RAW_POP 2 (Long POP)- TIME 1 - FINAL_September 19, 2024_19.26.csv",
              col_names=F,
              skip=3)

headers <- # import column names only
read.csv("~/Documents/R Files/POP2/Raw Data/RAW_POP 2 (Long POP)- TIME 1 - FINAL_September 19, 2024_19.26.csv",
         header = F,
         nrows = 1)

colnames(ip_locations_raw) <- unlist(headers) # add column names to dataframe

ip_locations_raw <- janitor::clean_names(ip_locations_raw, case="snake")

ip_locations_raw <- ip_locations_raw %>%  # add id col
  mutate(id = seq(from = 1, to = nrow(ip_locations_raw)),
         .before = start_date)
```

## IP Address Data

#### Source: https://github.com/ipinfo/sample-database/blob/main/IP%20Geolocation/ip_geolocation_sample.csv

```{r,eval=F}
ip_locations_raw <- read_csv("ip_geolocation_sample_edited.csv")
```

# Initial IP Address Analyses

```{r}
# duplicate ip addresses (count)
ip_locations_raw |>
  count(ip_address) |>
  filter(n > 1)

# duplicates ip addresses (data table)
dup_ip <- ip_locations_raw |>
  group_by(ip_address) |>
  filter(n() > 1) |>
  ungroup()                   

# duplicate locations (data table)
dup_coords <- ip_locations_raw |>
  group_by(location_latitude, location_longitude) |>
  filter(n() > 1) |>
  ungroup()

# add a count variable to dup_coords
dup_coords <- dup_coords |>
  add_count(location_latitude, location_longitude, name = "dup_coords_count")

# count coord frequency
loc_counts <- ip_locations_raw |>
  count(location_latitude, location_longitude, name = "freq") |>
  arrange(desc(freq))
```

```{r}
loc_counts$location_latitude  <- as.numeric(loc_counts$location_latitude)

loc_counts$location_longitude <- as.numeric(loc_counts$location_longitude)

# graph locations to find outside of the US
world <- map_data("world")

ggplot() +
  geom_map(data = world, map = world,
           aes(long, lat, map_id = region),
           fill = "grey95", color = "grey80", linewidth = 0.2) +
  geom_point(data = loc_counts,
             aes(x = location_longitude, y = location_latitude, size = freq),
             alpha = 0.6) +
  scale_size_area(max_size = 16, breaks = pretty_breaks(5)) +
  coord_quickmap() +
  labs(
    title = "Survey Response Approximate Locations (Point Size = Frequency)",
    x = "Longitude", y = "Latitude", size = "Responses"
  ) +
  theme_minimal(base_size = 12)

```

# Checking ISPs

## Prepping Data

## AC note: I'm not sure the separate_rows() is necessary because I don't think there would ever be a situation where data, at least from Qualtrics, would have multiple IPs in one cell. but i guess doesn't hurt to keep it

```{r}
# --------------------------------
# Split IP addresses into one per row
# --------------------------------
ip_data <- ip_locations_raw |>
  filter(!is.na(ip_address)) |>
  separate_rows(ip_address, sep = ",") |>
  mutate(
    query = stringr::str_trim(ip_address)
  ) |>
  dplyr::select(
    query,
    location_latitude,
    location_longitude
  )

ip_data
```

## APIs

### IP-API 

Batch lookup on ip-api (100 per request per ip-api free docs)

```{r}
to_query_objects <- function(ip_vec) {
  lapply(ip_vec, function(x) list(query = x))
}

lookup_batch_ipapi <- function(chunk_vec) {
  body_json <- jsonlite::toJSON(to_query_objects(unname(chunk_vec)), auto_unbox = TRUE)
  
  res <- httr::POST(
    url    = "http://ip-api.com/batch?fields=status,message,query,country,countryCode,region,regionName,city,lat,lon,isp,org,as,proxy,hosting,mobile",
    body   = body_json,
    encode = "raw",
    httr::add_headers(`Content-Type` = "application/json"),
    httr::timeout(10)
  )
  httr::stop_for_status(res)
  
  out <- jsonlite::fromJSON(httr::content(res, "text", encoding = "UTF-8"), flatten = TRUE)
  tibble::as_tibble(out)
}

chunks_100 <- split(ip_data$query, ceiling(seq_along(ip_data$query) / 100))

results_ipapi <- purrr::map_dfr(chunks_100, \(ch) {
  tryCatch(
    lookup_batch_ipapi(ch),
    error = function(e) {
      warning("ip-api batch failed: ", conditionMessage(e))
      tibble::tibble(status = "fail", message = conditionMessage(e), query = ch)
    }
  )
})
results_ipapi
```

### IP Info

(≤100 per request)

source: https://ipinfo.io/developers

```{r}
token <- "255a01dbca9d6e" # publicly available on their website

# look up on ipinfo.io - help function
lookup_ipinfo <- function(chunk_vec, token) {
  # ipinfo has a batch endpoint at /batch
  url <- paste0("https://ipinfo.io/batch?token=", token)
  
  # body is a JSON array of IPs
  body_json <- jsonlite::toJSON(as.list(chunk_vec), auto_unbox = TRUE)
  
  res <- httr::POST(
    url,
    body = body_json,
    encode = "raw",
    httr::add_headers(`Content-Type` = "application/json")
  )
  httr::stop_for_status(res)
  
  out <- jsonlite::fromJSON(httr::content(res, "text", encoding = "UTF-8"))
  
  # convert nested list to tibble
  tibble::enframe(out, name = "query", value = "info") %>%
    tidyr::unnest_wider(info)
}

ip_vec <- ip_data |>
  pull(query) |>                
  as.character() |>
  na.omit() |>
  unique()

# look up on ipinfo.io - run in chunks
chunks <- split(ip_vec, ceiling(seq_along(ip_vec) / 100))

results_ipinfo <- purrr::map_dfr(chunks, \(ch) {
  tryCatch(
    lookup_ipinfo(ch, token),
    error = function(e) {
      warning("Batch failed: ", conditionMessage(e))
      tibble(query = ch, error = conditionMessage(e))
    }
  )
})
results_ipinfo
```

### Free IP API

No Key - limited to 60 request/min 

**Note:** Sometimes I comment out the sys.Sleep() line since it makes it take awhile to run the code, but note that it won't get the IP info for all rows when this is the case.

## AC note: switch sys.sleep to 61 secs or something (and check to make sure this works) so this doesn't take so long

```{r}
lookup_freeipapi_one <- function(ip) {
  url <- paste0("https://freeipapi.com/api/json/", ip)

  res <- httr::GET(url, httr::timeout(15))
  httr::stop_for_status(res)

  x <- jsonlite::fromJSON(
    httr::content(res, "text", encoding = "UTF-8"),
    simplifyVector = TRUE
  )

  # drop only what you do not want
  x[c("timeZones", "zipCode")] <- NULL

  # keep only simple scalar fields
  x <- x[vapply(x, function(z) length(z) == 1 && !is.list(z), logical(1))]

  # force to character so bind_rows won't fail on mixed types
  x <- lapply(x, as.character)

  tibble::as_tibble(x) |>
    dplyr::rename(query = dplyr::any_of("ipAddress"))
}

lookup_freeipapi_bulk <- function(ip_vec) {
  purrr::map_dfr(as.character(ip_vec), function(ip) {
    tryCatch(
      lookup_freeipapi_one(ip),
      error = function(e) {
        tibble::tibble(
          query = ip,
          error = conditionMessage(e)
        )
      }
    )
  })
}

chunks <- split(ip_vec, ceiling(seq_along(ip_vec) / 60))

results_freeipapi <- purrr::map_dfr(chunks, \(ch) {
  tryCatch(
    lookup_freeipapi_bulk(ch),
    error = function(e) {
      warning("Batch failed: ", conditionMessage(e))
      tibble(query = ch, error = conditionMessage(e))
    }
    ,
        Sys.sleep(120)
  )
})
results_freeipapi
```

### IP Query

No key. Limit 10,000 IPs per batch.

**Note:** Could see if this method works for the other APIs and if so change to this since it's more concise

```{r}
ips_flat <- str_flatten(ip_data$query,collapse = ",")
url_ip_query <- 
  paste("https://api.ipquery.io/", ips_flat, sep = "")

results_ip_query <- GET(url_ip_query)
results_ip_query

results_ip_query <- fromJSON(rawToChar(results_ip_query$content))
results_ip_query

results_ip_query <- do.call(data.frame, results_ip_query)
results_ip_query <- results_ip_query %>% rename(query = ip)
```

**Note:** Having issue here where I get an error when running all together, but when I sepcifically run this chunk it works

## Combine all results

```{r}
combined_results <- results_ipapi |>
  dplyr::rename_with(~ paste0("ipapi_", .), -query) |>
  dplyr::full_join(
    results_ipinfo |>
      dplyr::rename_with(~ paste0("ipinfo_", .), -query),
    by = "query"
  ) |>
  dplyr::full_join(
    results_ip_query |>
      dplyr::rename_with(~ paste0("ipquery_", .), -query),
    by = "query"
  ) |>
  dplyr::full_join(
    results_freeipapi |>
      dplyr::rename_with(~ paste0("freeipapi_", .), -query),
    by = "query"
  )

combined_results
```

## Suspicious Host Flagging

**Note:** I looked into anycast, but not fully sure if that's something that would be suspicious. Sounds like it involves multiple servers showing up as the same IP address but not sure if that's something people would be using for suss survey things.

Including Tor since it seems to be used purposefully to hide your information on the internet

One var is character instead of logical for some reason:

```{r}
combined_results$freeipapi_isProxy <- as.logical(combined_results$freeipapi_isProxy)
class(combined_results$freeipapi_isProxy)
```


```{r}
host_cols <- combined_results %>% select(ipapi_hosting,ipapi_proxy,ipapi_hosting,ipquery_risk.is_tor,ipquery_risk.is_proxy,ipquery_risk.is_datacenter,freeipapi_isProxy)

# Source - https://stackoverflow.com/a/66365618
# Posted by Waldi, modified by community. See post 'Timeline' for change history
# Retrieved 2026-04-19, License - CC BY-SA 4.0

host_total <- # change to add mutate
combined_results %>%
  rowwise() %>% 
       summarize(host_total = 
                   sum(c(ipapi_hosting,ipapi_proxy,ipapi_hosting,ipquery_risk.is_tor,ipquery_risk.is_proxy,ipquery_risk.is_datacenter,freeipapi_isProxy,ipquery_risk.is_vpn),na.rm=T))

combined_results$host_total <- host_total

table(combined_results$host_total)
```

### Specific Names

**Note:** Could update these based on what we see with the VPNs/bot, but then obviously it's going to be effective lol. Not sure how to approach this. The ones I have here are just ones I've seen in datasets I've worked with, but I don't have any strong evidence that they're problematic.

# ideally change to make a loop going across all the ISP vars /more concise

```{r}
combined_results <- combined_results |>
  mutate(
    suspicious_host_ipapi_isp = if_else(
      str_detect(ipapi_isp, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool"),TRUE, FALSE, missing = FALSE))

combined_results <- combined_results |>
  mutate(
    suspicious_host_ipapi_org = if_else(                     
        str_detect(ipapi_org, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool"), TRUE, FALSE, missing = FALSE))

# in these data, ipapi_isp and ipapi_org seem to be the same

combined_results <- combined_results |>
  mutate(
    suspicious_host_ipapi_as = if_else(      
        str_detect(ipapi_as, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool"), TRUE, FALSE, missing = FALSE))

combined_results <- combined_results |>
  mutate(
    suspicious_host_ipinfo = if_else(
      str_detect(ipinfo_org, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|Dedicated.com|PacketHub S.A.|PPPoX Pool"),TRUE, FALSE, missing = FALSE))
                    
combined_results <- combined_results |>
  mutate(
    suspicious_host_ipquery = if_else( 
          str_detect(ipquery_isp.isp, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool"), TRUE, FALSE, missing = FALSE))

combined_results <- combined_results |>
  mutate(
    suspicious_host_freeipapi = if_else(
      str_detect(freeipapi_asnOrganization, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool"),TRUE, FALSE, missing = FALSE))

```

Creating one flagging variable across the different IP API fields:

```{r}
combined_results <- 
combined_results %>% mutate(suspicious_host_ipapi_final = 
                              case_when(suspicious_host_ipapi_isp == T | 
                                        suspicious_host_ipapi_org == T |
                                        suspicious_host_ipapi_as == T
                                      ~ TRUE,
                                      TRUE ~ FALSE))

combined_results$suspicious_host_ipapi_final
combined_results$suspicious_host_ipquery
combined_results$suspicious_host_freeipapi
```

```{r}
# susp_host_total <- # change to add mutate
# combined_results %>%
#   rowwise() %>% 
#        summarize(susp_host_total = 
#                    sum(c(suspicious_host_ipapi_final,suspicious_host_ipquery,suspicious_host_freeipapi),na.rm=T))


combined_results <-
combined_results %>%
  rowwise() %>% 
  mutate(susp_host_total = sum(c(suspicious_host_ipapi_final,suspicious_host_ipquery,suspicious_host_freeipapi),na.rm=T))

combined_results %>% select(susp_host_total,suspicious_host_ipapi_final,suspicious_host_ipquery,suspicious_host_freeipapi)
```

**Need to decide what reasonable threshold would be for this - of course people can change it for themselves though**

## Suspicious Location Flagging

### Incorrect Country

Here, since the premise is a study recruiting participants in U.S., we are just checking for *any* country codes listed as outside the U.S.

```{r}
combined_results <- combined_results |>
  mutate(
    geo_outside_us = (freeipapi_countryCode != "US" | ipquery_location.country_code != "US" | ipapi_countryCode != "US" | ipinfo_country != "US"))
combined_results$geo_outside_us
```

### Mismatched Cities

For regions and cities, since there is a more reasonable degree of error here, we will compare pairwise results between each API and count the number of mismatches. 

```{r}
# from Claude
# Helper: TRUE if either string contains the other (case-insensitive)
partial_match <- function(a, b) {
  mapply(function(x, y) {
    if (is.na(x) | is.na(y)) return(FALSE)
    grepl(x, y, ignore.case = TRUE) | grepl(y, x, ignore.case = TRUE)
  }, a, b)
}
```

```{r}
combined_results <- combined_results %>%
  mutate(
    city_match_1     = partial_match(ipquery_location.city, ipapi_city), # no
    city_match_2    = partial_match(ipquery_location.city, ipinfo_city), # no
    city_match_3 = partial_match(ipquery_location.city, freeipapi_cityName), # yes
    city_match_4 = partial_match(ipapi_city, ipinfo_city), # yes
    city_match_5 = partial_match(ipapi_city,freeipapi_cityName), # no
    city_match_6 = partial_match(ipinfo_city,freeipapi_cityName) # no
  )

combined_results %>% select(grep("city_match",names(combined_results)),ipquery_location.city,ipapi_city,ipinfo_city,freeipapi_cityName) %>% arrange(desc(city_match_n))
```

Creating a var showing number of pairwise matches:

```{r}
combined_results$city_match_n <- combined_results %>% select(city_match_1:city_match_6) %>% rowSums()

combined_results %>% select(city_match_n, city_match_1:city_match_6)
combined_results %>% select(city_match_n,ipquery_location.city,ipapi_city,ipinfo_city,freeipapi_cityName) %>% arrange(desc(city_match_n))

table(combined_results$city_match_n)
```

## AC note: issue here

the ones with city match n = 5 do match, but for some reason the two that are longer and have the same extra text are being flagged as mismatches. I tested it, and it doesn't seem to be due to the parantheses. 

but, for our purposes city match n = 5 is essentially in invalid result, and not meaningful, so i'll move forward without figuring it out.

city_match_n = 6 - all are the same
city_match_n = 5 - all cities are the same, but two have extra text that match one another, while the other two match one another and are contianed within the strings of the first two
city_match_n = 4 - not present (impossible?)
city_match_n = 3 - 1/4 is different from the other three
city_match_n = 2 - two pairs of matches
city_match_n = 1 - two match, the other two are different from all others
city_match_n = 0 - all cities differ


### Mismatched Regions

```{r}
combined_results <- combined_results %>%
  mutate(
    region_match_1     = partial_match(ipapi_regionName, ipinfo_region),
    region_match_2    = partial_match(ipapi_regionName, ipquery_location.state),
    region_match_3 = partial_match(ipapi_regionName, freeipapi_regionName),
    region_match_4 = partial_match(ipinfo_region, ipquery_location.state),
    region_match_5 = partial_match(ipinfo_region,freeipapi_regionName),
    region_match_6 = partial_match(ipquery_location.state,freeipapi_regionName )
  )

combined_results %>% select(grep("region_match",names(combined_results)),ipapi_regionName,ipinfo_region,freeipapi_regionName,ipquery_location.state) %>% arrange(desc(region_match_n))
table(combined_results$region_match_n)
```

Creating a var showing number of pairwise matches:

```{r}
combined_results$region_match_n <- combined_results %>% select(region_match_1:region_match_6) %>% rowSums()

combined_results %>% select(region_match_n, region_match_1:region_match_6)
```



#### Transform Geo Mismatch Data

```{r}
d_ips$city_match_n 
d_ips$region_match_n
```

##### City

Binning these counts into categories representing the severity of the issue, and then reverse scoring so that higher scores indicate greater mismatch.

Categories for the city data are as follows:

No concern (4-6 matches): 0 
Some concern  (2-3 matches): 1
Moderate concern (1 match): 2
Strong concern  (0 matches): 3

```{r}
d_ips <- 
d_ips %>% mutate(city_match_n_final = 
                   case_when(city_match_n  >= 4 ~ 0,
                             city_match_n == 2 | city_match_n == 3 ~ 1,
                             city_match_n == 1 ~ 2,
                             city_match_n == 0 ~ 3,
                             TRUE ~ city_match_n
                             ))
d_ips %>% select(city_match_n,city_match_n_final)
```

##### Region (State)

For the region data, I'm using the same categories as for city. Arguably, you could say that there should be a lower margin of error compared to the cities, so it would be more concerning if an IP address is categorized in multiple states - but looking through the states in this dataset I felt like the cities worked similarly well. We could also weight the states more heavily than cities in the final score, but I decided not to since a lot of the state mismatches I'm looking at in these data are neighboring states, which is less concerning to me. But we can change if needed.

Categories for the region data are as follows:

No concern (4-6 matches): 0 
Some concern  (2-3 matches): 1
Moderate concern (1 match): 2
Strong concern  (0 matches): 3

```{r}
d_ips <- 
d_ips %>% mutate(region_match_n_final = 
                   case_when(region_match_n  >= 4 ~ 0,
                             region_match_n == 2 | region_match_n == 3 ~ 1,
                             region_match_n == 1 ~ 2,
                             region_match_n == 0 ~ 3,
                             TRUE ~ region_match_n
                             ))
d_ips %>% select(region_match_n,region_match_n_final)
```

## Qualtrics RelevantID Data

For RelevantID fraud score, Qualtrics indicates that any score >30 is likely fraudulent and a bot. I'll also make a second flag to indicate any scores that are > 0.


```{r}
d_ips <- d_ips %>% mutate(rel_id_fraud_flag = ifelse(q_relevant_id_fraud_score >= 30, 
                                            TRUE,
                                            FALSE))
table(d_ips$rel_id_fraud_flag)

d_ips <- d_ips %>% mutate(rel_id_fraud_flag_0 = ifelse(q_relevant_id_fraud_score > 0, 
                                            TRUE,
                                            FALSE))
table(d_ips$rel_id_fraud_flag_0)

d_ips %>% filter(is.na(q_relevant_id_fraud_score)) # no missing scores
```



## Duplicate IP Addresses

### AC note: this is still going to lead to some inaccuracy since some SONA people will have the same IP address due to completing the survey literally in the same building.

## AC note: looks like there's an issue here? potetnailly due to duplicate IP addresses?

```{r}
# join to original data
d_ips <- ip_locations_raw |>
  mutate(ip_address = as.character(ip_address) |> str_trim()) |>
  left_join(combined_results, by = c("ip_address" = "query"))
```

```{r}
# duplicate IP address flag
d_ips  <- d_ips  |>
  add_count(ip_address, name = "ip_count") |>
  mutate(dup_ip = ip_count > 1)
table(d_ips$dup_ip)
```


### ISP Names

**Moved this to supplementary since for national data this would be really useful, but with our SONA data it's not helpful at all since almost everyone is completing the survey on UW-Campus and will show up with the same ISP.**

# AC note: not fully sure how to incorporate these. but, a way to automate this could be to calculate these counts, then feed in the ISP names with counts above a certain threshold into the previous code where we're flagging specific names. 

# AC note: **need to change this so that it doesn't flag common ISPs (e.g., AT&T) that are clearly legitimate companies**

```{r}
isp_counts <- bind_rows(
  combined_results |> count(ipapi_isp,  name = "n") |> rename(isp = ipapi_isp) |> mutate(source = "ipapi_isp"),
  combined_results |> count(ipinfo_org, name = "n") |> rename(isp = ipinfo_org) |> mutate(source = "ipinfo_org"),
    combined_results |> count(ipapi_org, name = "n") |> rename(isp = ipapi_org) |> mutate(source = "ipapi_org"),
      combined_results |> count(ipapi_as, name = "n") |> rename(isp = ipapi_as) |> mutate(source = "ipapi_as"),
        combined_results |> count(ipquery_isp.isp, name = "n") |> rename(isp = ipquery_isp.isp) |> mutate(source = "ipquery_isp"),
          combined_results |> count(freeipapi_asnOrganization, name = "n") |> rename(isp = freeipapi_asnOrganization) |> mutate(source = "freeipapi_asn")
)
isp_counts %>% arrange(desc(n))
```

Setting n for common ISPs to 0 so that they are not flagged.
(ISPs are taken from this list: https://en.wikipedia.org/wiki/List_of_broadband_providers_in_the_United_States)

```{r}
common_isps <-  
c("Comcast"	,
"Xfinity"	,
"Spectrum"	,
"Charter"	,
"AT&T"	,
"Verizon"	,
"T-Mobile"	,
"Cogent"	,
"Cox"	,
"Fidium"	,
"Lumen"	,
"CenturyLink"	,
"Mediacom"	,
"SpaceX"	,
"Starlink"	,
"TDS Telecom"	,
"Frontier"	,
"Windstream")
```
**Add code taking ISP names for col n > some threshold (5?) and putting them into a vector, then flagging any cases in the dataset where any ISP names contain any string that vector**

```{r}
# Source - https://stackoverflow.com/a/51112313
# Posted by MKR
# Retrieved 2026-06-05, License - CC BY-SA 4.0

library(stringr)

# Make sure to use \b around each word to avoid partial matching.
isp_counts$common_isp_test <-  str_detect(isp_counts$isp, pattern = paste(common_isps, sep="", collapse = "|"))
table(matches)

isp_counts %>% select(isp,common_isp_test) %>% arrange(desc(common_isp_test))
```

# LEFT OFF HERE - 6/5/2026

```{r}
isp_counts %>% mutate(n = case_when(
  grepl(isp, common_isps) == T ~ 0, 
  TRUE ~ n
))

```

## AC note: with all these threshold cut-offs, should set to calculate a % based on nrows in data

```{r}

```


```{r,eval=F}
isp_cutoff <- nrow(d_ips) * .05

isp_flag <- isp_counts %>% filter(count >= isp_cutoff) %>% select(query)
```


## Completion Times

#### note: will have to set to eval when using Qualtrics data

# AC NOTE: change this to either try to look at start/end times, and/or just remove very fast responders (but i've never figured out a good way to do this)

# add cutoff threshold for this

```{r,eval=F}
# check for clustering around the same completion time
time_clusters <- d_ips |>
  group_by(duration_in_seconds) |>
  summarise(count = n(), .groups = "drop") |>
  arrange(desc(count))

time_clusters
```

# Calculate Bot Liklihood Score

(as of now) bot scores range from 0 - 8

```{r}
d_ips <- d_ips |>
  rowwise() |>
  mutate(
    bot_score = sum(susp_host_total + geo_outside_us + city_match_n_final + region_match_n_final + dup_ip + rel_id_fraud_flag)
  )
table(d_ips$bot_score)
d_ips %>% select(bot_score,susp_host_total, geo_outside_us, city_match_n_final, region_match_n_final, dup_ip) %>% 
  arrange(desc(bot_score))
```

# prob change to automatically remove anyone with outside US location

# Screen bots

**Need to pick a threshold for bot scores, and then screen them out**

